### 2021-09-26 documents/sections/verbs.tex
slimmed down intro to section 4

\section{Resistant verbs in a comparative perspective}
\label{sec:verbs}
In \cref{sec:extensions}, six distinct extensions of personal prefixes into \gl{1}\gl{s_a_} territory were introduced, with certain verbs resisting the innovation.
The set of unaffected verbs was rather small in most cases, and there is a considerable etymological overlap between the (proto-)language-specific verb groups.
In this section, I present these verbs from a comparative perspective and discuss their reconstructibility.
Attentive readers will have noticed that certain verbs reoccurred in these lists, not only matching in meaning but also largely in form.
In this section, I will discuss these verbs from a comparative perspective.
\cref{sec:be} treats the copular verb \rc{eti}/\obj{a(p)} \qu{to be}, \cref{sec:say} \rc{ka(ti)} \qu{to say}, \cref{sec:go} \qu{ɨtə(mə)} \qu{to go}, and \cref{sec:come} \rc{(ət)jəpɨ} \qu{to come}; these are all verbs that \textcite{gildea2007greenberg} reconstructed as \gl{s_a_} verbs that were not derived from transitive verbs.
\cref{sec:godown} takes a look at \rc{ɨpɨtə} \qu{to go down}, which is resistant in \PTir and \PPek; \cref{sec:bathe} investigates \PPek \rc{ɨpɨ} \qu{to bathe}, \cref{sec:shit} \trio \qu{to defecate}, and \cref{sec:movement} the \akuriyo movement verbs.
The \obj{e}-initial verbs not affected by the extension of \rc{k-} in \akuriyo \pcref{sec:akuriyo} will not be discussed here, as they are a large and phonologically coherent group.

>>>>

\section{Resistant verbs from a comparative perspective}
\label{sec:verbs}
In \cref{sec:extensions}, we introduced six distinct extensions of personal prefixes into \gl{1}\gl{s_a_} territory, and identified verbs resistant to each innovation.
The set of unaffected verbs was rather small in most cases, and there is a considerable etymological overlap between the (proto-)language-specific verb groups.
In this section, we present these verbs from a comparative perspective and discuss their reconstructability.
\cref{sec:be} treats both roots of the copula \rc{eti}/\obj{a(p)} \qu{to be}, \cref{sec:say} \rc{ka(ti)} \qu{to say}, \cref{sec:go} \rc{ɨtə(mə)} \qu{to go}, and \cref{sec:come} \rc{(ət)jəpɨ} \qu{to come}; these are all verbs that \textcite{gildea2007greenberg} reconstructed as \gl{s_a_} verbs that were not derived from transitive verbs.
\cref{sec:godown} takes a look at \rc{ɨpɨtə} \qu{to go down}, which is resistant in \PTir and \PPek; \cref{sec:bathe} investigates \PPek \rc{ɨpɨ} \qu{to bathe}, \cref{sec:shit} \trio \qu{to defecate}, and \cref{sec:movement} the \akuriyo movement verbs.
The \obj{e}-initial verbs not affected by the extension of \rc{k-} in \akuriyo \pcref{sec:akuriyo} will not be discussed here, as they are a large and phonologically coherent group.
